A Reduced Order Model for Permeability Fields Using Singular Value Decomposition (SVD)

### 2018-04-14 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
updates

Furthermore, prior to the pre-processing required for evaluating the ArithMeanCase, HarmMeanCase and the PDFCase it is necessary to have an understanding of the whole domain and pre-define blocks with similar properties (\ie blocks $K1,~K2,~K3$ and $K4$) in this case. However, with the SVDCase, knowledge of blocks with similar properties is not required prior to the upscaling. Albeit, one has to select the upgrid resolution carefully, if the resolution is too large then there is the risk of losing relevant data in the interpolation (\ie feature elimination). The limits of the techniques used for the SVDCase is discussed in the author's future work.

Fig.~\ref{fig:BaseCase_Saturation} - \ref{fig:SVDCase_Saturation} presents the phase 1 saturation field simulation for all the cases at $t=0.15s,~t=0.30s,~t=0.50s,~t=1.15s,~t=1.75s$ and $t=2.95$. Fig.~\ref{fig:BaseCase_Saturation}, \ref{fig:ArithMeanCase_Saturation}, \ref{fig:HarmMeanCase_Saturation}, \ref{fig:PDFCase_Saturation}, \ref{fig:SVDCase_Saturation} show the simulation for the BaseCase, ArithMeanCase, HarmMeanCase, PDFCase and SVDCase, respectively. In Fig.~\ref{fig:BaseCase_Saturation} - \ref{fig:SVDCase_Saturation}(a) and (b), even though fluid is injected at the same rate across the left face it travels faster in $K1$ compared to $K2$. Fig.~\ref{fig:BaseCase_Saturation} - \ref{fig:SVDCase_Saturation}  (c) shows that fluid experience a resistance to flow at the interface between $K1$ and $K3$ which encourages the flow into $K4$ (Fig.~\ref{fig:BaseCase_Saturation} - \ref{fig:SVDCase_Saturation} (d) and (e)). Fig.~\ref{fig:BaseCase_Saturation} - \ref{fig:SVDCase_Saturation} (f) indicates preferential flow in $K4$ compared to $K3$.

>>>>

Furthermore, prior to the pre-processing required for evaluating the ArithMeanCase, HarmMeanCase and the PDFCase it is necessary to have an understanding of the whole domain and pre-define blocks with similar properties (\ie blocks $K1,~K2,~K3$ and $K4$) in this case. However, with the SVDCase, knowledge of blocks with similar properties is not required prior to the upscaling. Albeit, one has to select the upgrid resolution carefully, if the resolution is too large then there is the risk of losing relevant data in the interpolation. The limits of the techniques used for the SVDCase will be discussed in the author's future work.

\medskip
Figure~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation} presents snapshots of phase 1 (\ie injected or displacing fluid) saturation field for all studied cases. Figure~\ref{fig:BaseCase_Saturation}, \ref{fig:ArithMeanCase_Saturation}, \ref{fig:HarmMeanCase_Saturation}, \ref{fig:PDFCase_Saturation}, \ref{fig:SVDCase_Saturation} show the simulation for the BaseCase, ArithMeanCase, HarmMeanCase, PDFCase and SVDCase, respectively. In Fig.~\ref{fig:BaseCase_Saturation} - \ref{fig:SVDCase_Saturation}(a) and (b), even though fluid is injected at the same rate across the left face it travels faster in $K1$ compared to $K2$. Fig.~\ref{fig:BaseCase_Saturation} - \ref{fig:SVDCase_Saturation}  (c) shows that fluid experience a resistance to flow at the interface between $K1$ and $K3$ which encourages the flow into $K4$ (Fig.~\ref{fig:BaseCase_Saturation} - \ref{fig:SVDCase_Saturation} (d) and (e)). Fig.~\ref{fig:BaseCase_Saturation} - \ref{fig:SVDCase_Saturation} (f) indicates preferential flow in $K4$ compared to $K3$.
